---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# clust431

<!-- badges: start -->
<!-- badges: end -->

The goal of clust431 is to do k-means clustering and hierarchical clustering.

## Installation

You can install the released version of clust431 from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("clust431")
```

## Example for k_means()

This is a basic example which compares the original kmeans function to the one made for lab 7

```{r example}
library(clust431)
library(tidyverse)

iris2 <- iris %>%
    select(Sepal.Length, Sepal.Width)
k_means(iris2, 3, PCA = F)

```

The chunk below is comparing the results of my function from above to the built-in function. 

```{r}
actual <- kmeans(iris2, 3)
actual
actual$totss - actual$betweenss
actual$totss
```

As we can see, we get the same SSE, clustering vectors, and cluster means. Our function gives SSE straight up, but there is more calculations needed. That being said, the built-in function has much more information. 

## Example for hier_clust()

This is a basic example which compares the actual hier_clust function to the one made for lab 7

```{r}
iris3 <- iris %>%
  select(-c(Species))
b = hier_clust(iris3, k=150, method = 'euclidean')
head(b, 6)
a = hclust(dist(iris3))
head(a$merge, 6)
```

```{r}
hier_clust(iris3, k=3, method = "manhattan")
```

